\section{Summary}

Providing better QoS while maintaining lower resource lease costs in a PaaS system is extremely challenging for a reactive, threshold-based auto-scaling solution. Even though proactive solutions can overcome these challenges, they are dependent on highly accurate prediction mechanisms. Existing workload prediction techniques which mainly focus on single, offline-trained models do not work well with heterogeneous PaaS applications with drastically different and varying workload patterns. To address this problem, we proposed an ensemble prediction technique that combines predicted values from different time series prediction techniques. We train each model in real time (as in a functional auto scaler) and combine the forecasts based on the weights calculated from the inverse errors of fitted values for the training data. Rather than taking only the last forecasting error or the mean over all the past errors, we used exponential smoothing to fit the past forecasting error of each model. We implemented the proposed ensemble technique using four popular forecasting models and tested it on three publicly available datasets, two cloud workload dataset, and the Google cluster dataset. Experimental results show that the proposed ensemble prediction technique produces the least error in several datasets and never perform worse than any of the individual prediction methods in other cases. As the proposed forecasting method should generate the forecast within a bounded time, we limit the size of the input training window. Further work is needed to identify the optimum input window size that would maximize accuracy while not violating the temporal restrictions on calculating the forecasts in real-time.